\documentclass[../00_Main.tex]{subfiles}
\begin{document}

The system evaluation was conducted using a modular verification framework:
\begin{itemize}
    \item The \textbf{Software Subsystem} was evaluated for latency and waveform spectral purity.
    \item The \textbf{Hardware Transduction} was validated using gelatine cubes and controlled input signals.
    \item The \textbf{Signal Acquisition Subsystem} was tested for signal integrity and noise levels using controlled input signals.
    \item The \textbf{Closed-Loop System} was assessed by integrating the signal generation and a simplified form of the hardware module, comparing the output using the acquisition module to verify real-time performance.
\end{itemize}

The validation process utilized both laboratory instrumentation and the developed software subsystem to generate controlled input signals.

Throughout the experimental validation phase, homogeneous gelatine-based prototypes were used as the primary physical test platform. This approach was adopted as a practical stepping stone before implementing the complete bilayer architecture in the future, allowing for systematic characterization of the conductive medium, validation of signal transduction methods, and assessment of the closed-loop system performance under controlled conditions. The use of homogeneous prototypes simplified the fabrication process and reduced sources of variability during initial testing, while still providing a physically realistic conductive medium for signal propagation experiments. Results obtained from these homogeneous configurations inform the interpretation of the system's practical behavior and establish baseline performance metrics for the integrated platform.

The project utilizes the \textbf{Phantom Head Numerical Model} as the integration reference for a two-layer phantom head constructed following the methods described in Section~\ref{sec:materials_and_methods}. This numerical model serves as a theoretical counterpart to the physical system, providing a reliable first-order approximation of its expected behavior. Within this context, the theoretical validation demonstrates that, given the proven performance of the individual components, the combined system exhibits behavior consistent with the intended design and supports a preliminary assessment of the feasibility of the proposed architecture when the modules are integrated in a bilayer phantom.

\subsection{Materials: Electrical Behavior and Suitability for Phantom Construction}

Based on the state-of-the-art review, a bilayer phantom architecture was identified as the most promising approach for future implementations, featuring an external conductive shell and an internal conductive volume. While this bilayer design informed the \gls{cad} modeling and system architecture described in the Materials and Methods section, the experimental validation conducted in this work focused on homogeneous gelatine-based prototypes as a practical starting point. The material characterization strategy reflects this approach, prioritizing experimental assessment of the conductive medium that forms the basis of both homogeneous and bilayer configurations.

The conductive medium selected for characterization is a saline--gelatine formulation, which is readily available, inexpensive, and highly customizable through formulation parameters. This material serves as the primary conductive layer in homogeneous prototypes and would constitute the internal volume in a future bilayer implementation. For this reason, the experimental characterization efforts focused on assessing its electrical behavior, tunability, and reproducibility in the context of phantom construction. Rather than aiming at a precise metrological determination of conductivity values, the experiments were designed to qualitatively evaluate how the electrical response of the material evolves with ionic concentration, and whether these properties can be reliably reproduced across fabrication batches.

For completeness, the bilayer design concept envisions an outer shell fabricated using commercially available conductive polymer, selected to balance electrical performance, mechanical printability, and practical accessibility within an academic prototyping context. While custom composite formulations could, in principle, be developed to achieve tighter control over electrical properties, such approaches would significantly increase fabrication complexity and cost. For this reason, a commercially available conductive PLA was identified as a representative and reproducible choice for future work, with electrical properties largely determined by the material specification and the additive manufacturing process itself. Accordingly, its characterization in this work relies primarily on manufacturer data and existing literature rather than on direct experimental validation.

\paragraph*{Electrical Behavior and Experimental Behavior of the Gelatine Layer}

The impedance measurements obtained for gelatine samples with varying NaCl concentrations
exhibit the expected behavior of an electrolytic medium.
The addition of salt increases the density of free ions within the matrix, leading to a
reduction in the overall electrical impedance across the analyzed frequency range.
This behavior is illustrated in Figure~\ref{fig:gelatine_results}, particularly when
comparing formulations with and without added NaCl.

The NaCl concentrations evaluated in these experiments are higher than those required for
the specific objectives addressed in this work.
This choice reflects two practical considerations.
First, the selected concentrations provide reference points comparable to values commonly
reported in the literature.
Second, the experimental setup imposed constraints on the preparation and control of
low-concentration solutions.
At lower concentrations, uncertainties associated with solution formulation and handling
became more prominent, resulting in larger relative variability in the measured impedance
values.
Within this range, the higher concentrations enabled more consistent measurements and a
clearer assessment of material trends.

Temperature effects also played a non-negligible role in the observed results.
Due to uncontrolled environmental conditions, temperature variations occurred during the
measurement process, which may introduce additional variability between measurements.
Since the electrical conductivity of aqueous gels is known to be temperature-dependent,
this factor represents an additional source of uncertainty when interpreting absolute
impedance values.

In addition, the small sample size and experimental geometry introduce boundary-related
effects.
In particular, the formation of an electrical double layer (EDL) at the electrode--gel
interface affects impedance measurements under the present conditions.
At the tested salt concentrations, ambient temperatures, and short electrode separations,
EDL-related phenomena introduce an effective interfacial capacitance, contributing to both
the measured impedance magnitude and the observed phase angle.
This behavior is consistent with the non-zero phase shifts observed in
Figure~\ref{fig:gelatine_results}, especially at low frequencies.

An additional feature of the results is the non-monotonic relation of impedance magnitudes
at certain frequencies, where the 2.5\% NaCl sample exhibits higher impedance values than the
sample without added salt.
This behavior suggests the presence of secondary effects related to material composition.
Possible contributors include residual ionic content in the gelatine or the deionized water
used during sample preparation.
Future iterations could consider alternative materials, such as ballistic gel, whose
composition is typically more controlled and reproducible.
This option, however, would increase the overall cost of the phantom and must be evaluated
in relation to system requirements.

All samples were prepared using the same batch of base materials.
As a result, any systematic offsets in material composition are shared across all
formulations.
Under these conditions, samples with identical compositions exhibited consistent impedance
behavior across repeated measurements.
The relative deviation between independent realizations of the same formulation remained
below 10\%, indicating a high degree of reproducibility.
This level of consistency is particularly relevant for phantom applications, where stable
and repeatable material properties are essential for experimental comparability.

Moreover, when considered in terms of order of magnitude, relative trends between
formulations, and frequency dependence, the measured impedance values show qualitative
agreement with those reported by Owda~\emph{et al.}~\cite{Owda2020}.
This agreement indicates that the dominant conduction mechanisms governing the electrical
behavior of gelatine are consistently captured.

Beyond the selection of a specific gelatine formulation, the experiments demonstrate that
the electrical properties of gelatine depend systematically on salt concentration and can
be reproduced consistently across independent realizations.
For a desired target impedance or conductivity, an appropriate formulation can therefore
be designed and reliably re-prepared, provided that operating conditions---particularly
temperature---are taken into account.
From a phantom design perspective, this combination of tunability and reproducibility is a
key requirement, as it enables both controlled adjustment of material properties and
repeatable experimental conditions.
Within this framework, gelatine remains a plausible and adaptable material for the
construction of the proposed phantom, offering sufficient flexibility and stability for
systematic experimental use.

Validation experiments conducted with the Open EEG Phantom confirmed that the gelatine-based conductive medium supports effective signal propagation within a full-scale anthropomorphic geometry. The successful measurement of software-controlled waveform patterns at the phantom surface demonstrates that electrical signals originating from internal excitation points are reliably transmitted through the homogeneous gelatine volume to surface electrodes. These results validate the material's suitability for \gls{eeg} phantom applications and establish the homogeneous configuration as a functional baseline for subsequent implementation of the bilayer architecture.

\paragraph*{Material Cost Estimate}
Having established the feasibility of the selected materials for the proposed phantom
design, an approximate cost estimate can be derived for a single realization.

Costs are reported using typical purchase units and current market prices, and the resulting
estimate is summarized in Table~\ref{tab:phantom_cost}.
\begin{table}[h]
\centering
\caption{Estimated material costs for a single phantom realization.}
\label{tab:phantom_cost}
\begin{tabularx}{\textwidth}{X S X}
\hline
\textbf{Material} & \textbf{Estimated Cost} & \textbf{Note} \\
\hline
Salt (1 box) & \$2 & Conductivity tuning; readily available \\
Deionized water (5~L)
& \$11 & Solvent for gel preparation and conductivity control \\

Gelatine (1 kg, flavorless)
\href{https://www.mercadolibre.com.ar/gelatina-sin-sabor-x-1-kg-cocina-reposteria/up/MLAU144145680}{(\underline{Link})}
& \$20 & Food-grade, unflavored \\

Conductive PLA filament (1 spool)
\href{https://www.idealo.fr/prix/203614180/proto-pasta-pla-filament-1-75mm-500g-magnetic-iron.html}{(\underline{Link})}
& \$50 & Upper shell half material \\

Non-conductive PLA filament (up to 2 spools)
\href{https://www.arianeplast.com/fr/pla-format-1-kg/104-plablanc4043d-pla-blanc-4043d-3d-filament-arianeplast-fabrique-en-france-1kg.html}{(\underline{Link})}

& \$36 & Structural components \\
Silicone / gasket material & \$5 & Waterproofing of head sealing interface \\

Electrical components & \$35 & --- \\

External sound card
\href{https://www.amazon.com/YEY-Loop-Back-Support-standalone-Software/dp/B0BQ6W9N9X}{(\underline{Link})}
& \$24 & Only if no 7.1 sound card is available in the system and 8 channels are required \\
\hline
\end{tabularx}
\end{table}

The reported values correspond to the items required to build the system. The estimate therefore excludes realization-dependent fabrication and assembly costs, including equipment access and use (e.g., 3D printer acquisition or amortization, maintenance, print-time and energy consumption), printing losses (failed prints and reprints), and specialized tooling. Likewise, outsourced fabrication services (e.g., third-party printing) and procurement logistics (shipping and potential import fees) are not included.
Overall, the estimated total cost is approximately \$159 for the baseline build, increasing to approximately \$183 only if an external multichannel sound card is required.


Current commercial phantom systems typically involve substantially higher costs. Injection molding tooling costs are reported in the range of \$6,700 to \$27,000, with individual phantom units priced between \$400 and \$640~\cite{akor-2025}.


\subsection{Numerical Phantom Validation and System-Level Implications}

The Phantom Head Numerical Model was constructed to capture the dominant electrical behavior of a two-layer conductive phantom head while remaining consistent with the methodological scope and practical constraints of the project. The modeling choices reflect a deliberate balance between physical realism and controlled complexity, with the objective of supporting system-level validation rather than producing a fully resolved digital replica of the physical phantom.

Several aspects of the physical phantom were intentionally simplified or excluded from the numerical representation. In particular, the conductive cranial shell was modeled as a homogeneous and isotropic layer, despite the fact that an additively manufactured shell would exhibit anisotropy and microstructural variability arising from printing parameters such as infill pattern, infill density, layer orientation, extrusion temperature, and inter-layer bonding. These features introduce internal geometric and material heterogeneity that is not explicitly resolved in the numerical domain. Their omission is intentional, as their influence on the electrical behavior of the system is expected to be addressed experimentally through calibration rather than through further numerical refinement.

Similarly, the conductive volume representing the internal medium was assumed to be homogeneous. In practice, its electrical properties may vary locally due to temperature gradients, aging effects, or small-scale imperfections introduced during preparation and solidification. For example, exposure to ambient heat or localized heating during operation could affect gelatine conductivity, while residual air inclusions or minor concentration gradients may arise during casting. Such effects are difficult to characterize a priori and are not meaningfully captured within a simplified finite element representation.

Electrode interfaces were also idealized in the numerical model. Electrodes were represented with perfectly defined geometries and ideal electrical contact with the surrounding medium. In a physical realization, electrode–surface contact impedance, surface roughness, connector tolerances, and minor geometric imperfections introduce additional variability. These effects are inherently electrode-specific and time-dependent, and are therefore more appropriately handled through experimental calibration than through explicit numerical modeling.

Finally, extreme mesh refinement was deliberately avoided. While increased resolution would reduce discretization error, it would not eliminate the aforementioned sources of physical variability and would significantly increase computational cost. Given that the numerical model is intended to provide a first-order approximation and feasibility assessment rather than exact prediction, the chosen level of refinement is sufficient to capture the relevant system behavior without introducing unnecessary detail.

Within these assumptions, the numerical model provides a coherent and controlled representation of the phantom head that is suitable for evaluating forward responses, constructing transfer operators, and assessing reconstruction performance.

\subsubsection{Mesh Quality Comparison}
To assess whether the numerical discretization is consistent across geometries of different complexity, mesh quality metrics were evaluated for both the analytical spherical benchmark and the phantom-head model. The purpose of this comparison is not to claim identical mesh quality, but to verify that the meshing strategy behaves robustly when transitioning from an idealized geometry to a realistic head-shaped domain.

Global quality indicators, including SICN, SIGE, and gamma, exhibit comparable average values in both meshes. In all cases, the mean values remain within a range typically associated with stable finite element performance, indicating that the overall element quality is preserved despite the increased geometric complexity of the phantom-head model. This result confirms that the selected meshing parameters provide a consistent discretization baseline across both configurations.

The primary differences between the two meshes are observed in the distribution extremes rather than in their central tendencies. In particular, the phantom-head mesh exhibits lower minimum gamma values than the spherical benchmark. These worst-case elements are spatially localized and can be traced to specific geometric features introduced during \gls{cad} construction, such as sharp transitions or small offsets required to merge external anatomical features into the base geometry. Resolving these narrow regions necessitates the presence of very small elements, which locally degrade element shape metrics.

Importantly, these low-quality elements appear as isolated outliers and do not reflect a systematic degradation of mesh quality. Their limited spatial extent means they do not dominate the numerical behavior of the system or significantly influence global solution stability. In contrast, the bulk of the mesh retains quality metrics comparable to those of the spherical benchmark.

As a consequence of this similarity in global mesh quality, it is reasonable to assume that the numerical error introduced purely by discretization is of the same order of magnitude across both geometries, independent of the availability of an analytical solution. This observation provides a consistent basis for interpreting subsequent numerical results, while the quantitative assessment of discretization error is addressed separately in the following sections.


\subsubsection{Benchmarking Geometry: Discretization Error Analysis}

The analytical spherical benchmark provides a controlled setting to analyze the discretization error introduced by the numerical formulation independently of geometric complexity. Since an analytical solution is available for this configuration, the benchmark allows a direct comparison between the numerical solution and the exact reference, making it possible to characterize both the magnitude and spatial structure of the numerical error.


Table~\ref{tab:sphere-error-distributions} summarizes distribution statistics of the absolute discretization error computed over all sampled points for each conductivity configuration and spatial region. A first observation is that the mean error values appear relatively large when computed over the full domain, with values on the order of $10^{-1}$~V However, this interpretation is misleading if considered in isolation.

In all cases, the median error is several orders of magnitude smaller than the mean, with values on the order of $10^{-5}$--$10^{-8}$~V. This large discrepancy between mean and median indicates a strongly skewed error distribution, dominated by a small number of localized high-error regions. The 95th percentile values further support this interpretation, showing that the bulk of the domain exhibits significantly lower error than suggested by the mean alone.

When restricting the analysis to the outer region of the domain---which includes the external measurement surface together with a thin adjacent volume encompassing the material interface---the median error decreases even further, reaching values well below $10^{-6}$~V. This behavior is expected, as the material interface introduces localized discretization error due to conductivity transitions, while the error at the surface itself remains very low. Considering the combined region therefore provides a conservative but representative estimate of the numerical accuracy in the vicinity of practical measurements.

\paragraph*{Spatial Localization of the Error}\\

The spatial structure of the discretization error is illustrated in Figure~\ref{fig:sphere-error-field}, which shows the absolute error field in the central region of the sphere. High-error regions appear as isolated patches localized near internal interfaces and regions of strong field gradients. These locations are consistent with areas where the numerical solution is most sensitive to discretization.

Away from these localized regions, the error rapidly decreases, resulting in a largely low-error background across the majority of the domain. This spatial localization explains the discrepancy between mean and median statistics and confirms that the discretization error is not uniformly distributed throughout the domain.

Further insight is provided by the radial distributions shown in Figures~\ref{fig:sphere-error-radius} and~\ref{fig:sphere-error-radius-zoom}. Figure~\ref{fig:sphere-error-radius} shows the absolute discretization error as a function of radius across the entire domain. The error reaches its maximum near the inner radius, where it remains on the order of $10^{-4}$~V, and then decreases as the radius increases. 

As the radius approaches the external boundary, the error drops by several orders of magnitude. This behavior is shown more clearly in Figure~\ref{fig:sphere-error-radius-zoom}, which focuses on the outer region ($r \geq 79\,\mathrm{mm}$), including the external surface and a narrow shell of the adjacent material. In this region, the absolute error remains on the order of $10^{-6}$~V or lower and continues to decrease toward the boundary. This confirms that, despite the presence of material interfaces, the numerical solution is particularly accurate in the region relevant for surface-level measurements.

Taken together, these results show that the discretization error in the analytical benchmark is confined both spatially and statistically. Large error values are restricted to localized regions associated with strong gradients and material transitions, while the majority of the domain---and in particular the outer shell surrounding the measurement surface---exhibits substantially lower error.

Although a nonzero discretization error is unavoidable even in this analytically ideal configuration, its magnitude and localization provide a practical reference for estimating the numerical uncertainty associated with surface-level measurements. The benchmark therefore establishes a consistent error scale inherent to the adopted methodology, which can be used to interpret numerical results obtained in more complex geometries.

On this basis, surface-level measurements and digitally sampled potentials obtained from the phantom-head model can be considered reliable up to this estimated numerical uncertainty, providing a sound basis for the subsequent analysis.

\subsubsection{Phantom-Head Model: Numerical Analysis and Interpretation}
The numerical simulations of the phantom-head geometry were performed using the same governing equations, numerical formulation, and discretization strategy previously validated on the analytical benchmark. Consequently, the numerical behavior observed in the head model is interpreted within the same methodological framework, with the primary difference arising from the increased geometric complexity of the domain rather than from changes to the numerical pipeline itself. This continuity allows the results obtained for the phantom head to be analyzed in light of the discretization characteristics already established for the benchmark geometry.

Before examining quantitative metrics, the potential distributions obtained in the phantom-head simulations were inspected qualitatively to verify the absence of obvious numerical artifacts. Away from the electrodes, the potential fields vary smoothly and exhibit gradual spatial changes, while steeper gradients are observed in the immediate vicinity of the electrodes, where stronger local fields are expected. No discontinuities, oscillatory patterns, or nonphysical behavior were observed near boundaries or material interfaces. Although no analytical solution is available for direct comparison in this geometry, this qualitative inspection serves as a basic sanity check on the numerical solution.

Surface potential maps further support this qualitative assessment. The spatial patterns observed on the outer surface reflect the position of the activated electrode, with regions of higher and lower potential aligned with its location. The sign of the surface response is consistent with the polarity of the applied excitation, and the overall magnitude of the surface potentials scales as expected with the stimulus amplitude. These observations do not constitute a formal validation, but they indicate that the numerical solution behaves coherently and in line with qualitative expectations, providing confidence for the subsequent quantitative analysis.

A key feature of the phantom-head response is the strong attenuation introduced by volume conduction. Internal electrode excitations on the order of one volt result in surface potentials on the order of tens of millivolts, with peak values around $55$~mV depending on electrode location. This level of attenuation is consistently observed across simulations and is qualitatively consistent with the strong signal decay expected in a head-sized conductive volume. From a practical perspective, this attenuation establishes the scale of measurable signals and provides important context for interpreting both numerical and experimental uncertainties.

In particular, small relative discrepancies in the reconstructed excitation vector are further reduced when mapped to surface potentials. As a result, the absolute differences between reconstructed and reference surface signals remain well below the numerical uncertainty estimated from the benchmarking geometry. The same attenuation mechanism also implies that small perturbations introduced at the level of signal generation or acquisition—such as noise or hardware-related variability—are likewise suppressed at the measurement surface. Within the limits imposed by the numerical method, these effects do not lead to practically significant deviations in the surface-level signals considered here.

All numerical results presented for the phantom-head model depend implicitly on the assumed electrode geometry, orientation, and positioning. In the simulations, electrodes were placed in an idealized and highly controlled manner: each electrode was positioned at the center of its corresponding wire guide, aligned perpendicular to the guide opening, and located precisely at the interface defined by the start of the sleeve region. This digital placement ensures perfect alignment and repeatability across simulations and removes variability associated with positioning or orientation.

In a physical implementation, deviations from this idealized configuration are unavoidable and would modify the local field distribution and the resulting surface potentials. Variations in electrode position, orientation, or depth are therefore expected to introduce measurable changes in the system response. The numerical results presented here should thus be interpreted as representing an ideal reference configuration, against which the effects of physical tolerances and calibration can later be assessed.

Within these assumptions, the phantom-head numerical model provides a coherent and internally consistent description of system behavior. The observed attenuation, the bounded impact of reconstruction and measurement-related uncertainties at the surface, and the qualitative correspondence between stimulus configuration and surface response support the feasibility of the proposed design and establish a reliable numerical context for the analysis of the forward operator and reconstruction performance presented in the following sections.

\subsubsection{System Stability and Representation}
Beyond the analysis of field distributions and signal attenuation, the numerical phantom-head model also enables an assessment of system stability from a linear-systems perspective. The relationship between internal electrode excitations and surface measurements can be represented by a forward operator, constructed from the simulated responses of the head geometry. Analysis of this operator provides insight into the numerical properties of the system and its suitability for both prediction and reconstruction tasks.

When considering the full set of nine internal electrodes, the resulting system was found to be moderately ill-conditioned. In practical terms, this means that while the forward mapping remains well defined, small perturbations in the input or measurement space—arising from numerical error, noise, or modeling uncertainty—can be amplified during inversion. This behavior is expected in conductive volume problems, where electrode responses are spatially correlated and the system does not exhibit strong orthogonality between control channels.

To improve numerical robustness, reduced representations of the system were therefore explored. By restricting the operator to a subset of eight electrodes, a significant improvement in numerical stability was achieved, while the loss in nominal accuracy remained limited. This represents a favorable trade-off: a relatively small reduction in control dimensionality leads to a substantial gain in stability and robustness. From a system-design perspective, this trade-off is highly advantageous, as it prioritizes reliable operation over marginal theoretical resolution.

This numerical observation directly informed design decisions beyond the purely mathematical model. In particular, the choice to represent the system using an eight-electrode configuration aligns naturally with the physical constraints and implementation of the phantom hardware, as illustrated in Figure~\ref{fig:hardware_system}. Rather than treating the reduced operator as a numerical workaround, it becomes an integral part of the system architecture, linking simulation results to practical implementation.

The characterization of the forward operator developed in this work provides a practical
interface between the phantom-head system and its numerical description.
Beyond its role in model validation, this characterization enables the systematic design
and interpretation of experimental configurations.

In a forward sense, the identified mapping between internal electrode excitations and
surface potentials allows expected measurements to be estimated at predefined locations on
the phantom surface corresponding to points of the international 10--20 electrode system.

For a given set of internal input signals, the forward model defines the surface potentials
that should be observed at specific locations, providing a reference for calibration and
for consistency checks between predicted and measured data.

The same system characterization also enables an inverse, control-oriented use case.
Starting from a desired signal value or waveform at one or more surface locations, the
inverse operator can be used to determine the internal electrode excitations required to
produce such a response.
This allows experimental test cases to be specified directly in terms of surface-level
behavior, with the corresponding actuator inputs obtained through the identified transfer
model.

In this sense, the numerical characterization of the phantom head is not limited to
descriptive analysis.
It defines a transferable relationship between internal actuation and surface observation
that can be used for calibration, validation, and controlled experimentation.
The reconstruction results obtained with the reduced eight-electrode operator indicate
that this mapping remains well behaved across the tested scenarios, supporting its use as a
reliable intermediary between desired surface signals and internal excitation patterns.

This characterization could be directly integrated into the software platform by loading
the forward operator \(A\) and, when required, its pseudoinverse \(A^{\dagger}\).
Within such an interface, the columns of the operator would be explicitly associated with
the eight internal actuation channels of the phantom, corresponding to the physical signal
generation layout: rear left/right, center left/right, subwoofer left/right, front left/right,
and side left/right channels.
The rows of the operator would, in turn, be mapped to surface measurement locations,
identified by their corresponding 10--20 electrode labels (e.g., Fp1, Oz, T6).


In a forward-prediction mode, a measurement view could be linked to a selected surface
location (for example, Oz), allowing the application to display the signal that should be
measured there for a given set of actuator inputs.

Conversely, an inverse mode could allow the user to specify a desired signal at a selected
surface location---for instance, imposing a sinusoidal waveform at Oz---and automatically
compute the corresponding actuator values required to reproduce that response.
In this configuration, the application would act as an interface to the identified system
model, translating between surface-level signal specifications and internal excitation
parameters in a mathematically consistent manner.

The integration of this model-driven interaction into the software platform is therefore
naturally identified as a direction for future development.

\subsection{Desktop Application}

The system was assessed based on its ability to generate synthetic electrophysiological signals, acquire real-time data from hardware interfaces, and manage session persistence.

\subsubsection{System Architecture and Performance}

The core signal generation engine has a robust deterministic behavior, essential for phantom testing. By utilizing a \texttt{gevent}-based asynchronous architecture, the system achieves a consistent sampling rate of $1\,\text{kHz}$ ($1\,\text{ms}$ intervals). A critical component of this implementation is the maintenance of phase continuity; the use of phase accumulators prevents signal discontinuities during dynamic parameter adjustment (e.g., changing frequency or amplitude in real-time).

The integration of modern web technologies (React and TypeScript) with a Python Flask backend provides a responsive user interface without compromising computational performance. The frontend visualization, utilizing buffered canvas rendering, maintains frame rates between 30 and 60 FPS even when rendering all 8 channels simultaneously.

\subsubsection{Signal Processing and Data Acquisition}

The platform supports two distinct operational modes: synthetic generation and hardware acquisition.

\paragraph*{Signal Fidelity and Export}
The recording subsystem ensures high data integrity. Sessions are serialized into a multi-format ZIP bundle containing raw CSV data, JSON metadata, and WAV audio reconstruction. The export pipeline preserves the $44.1\,\text{kHz}$ audio fidelity and ensures that all parameter changes are logged synchronously with the signal data. This allows for accurate post analysis and session replay.

\subsubsection{Hardware Constraints and Design Trade-offs}

\paragraph*{Audio Output Configuration}
While the software internally generates 8 independent channels with proper phase alignment, the physical output is constrained by standard consumer hardware, which typically supports only stereo (2-channel) DACs. The current implementation relies on an operating system-level abstraction to mix these signals. For full 8-channel phantom stimulation, if the user does not have a 7.1 sound card, the system requires an external multi-channel sound card. This is a hardware dependency rather than a software limitation, but it impacts the utility for users without specialized audio equipment.

\paragraph*{Memory Management}
The current session management strategy stores active recording data in volatile memory (RAM). While this reduces I/O latency during recording, it imposes a scalability limit. For an 8-channel system, the memory footprint grows linearly with time. Extended sessions (e.g., exceeding one hour) may risk memory exhaustion. A streaming-to-disk architecture would be required to support indefinite recording durations.

\subsection{Future Work}

Several areas have been identified for future development to enhance the software system's robustness and analytical capabilities.

\textbf{Scalability and robustness:} To address the memory constraints mentioned above, future iterations should implement paginated disk buffering. Additionally, error handling should be enhanced, particularly regarding audio subsystem failures. A more granular exception-handling strategy is necessary when hardware peripherals fail.

\textbf{Integration with forward model:} The numerical phantom head model developed in this work provides a systematic mapping between internal electrode signals and surface potentials. Future software versions should integrate this model, allowing users to specify desired surface signals and automatically compute the corresponding internal values using the forward and inverse operators, or visualize expected surface responses for given internal inputs.

\textbf{Advanced signal analysis:} The current visualization is limited to the time domain. Future expansions should include frequency-domain analysis tools, such as real-time Fast Fourier Transform (FFT) and Power Spectral Density (PSD) plots, to provide immediate feedback on signal spectral content.

\textbf{Extended hardware support:} While currently optimized for OpenBCI, the architecture is designed to be extensible. Future integration with the Lab Streaming Layer (LSL) protocol would significantly broaden hardware compatibility, allowing the software to interface with a wider range of \gls{eeg} devices and synchronization triggers.

For the physical phantom system, the following improvements are proposed:

\textbf{Hardware signal amplification:} For calibration purposes, integrating the designed amplification module between the phantom output and the acquisition system would enhance signal quality in extended time periods, countering the effects of material degradation over the days. This would mitigate the effects of attenuation and improve the signal-to-noise ratio, particularly for low-amplitude test signals.

\textbf{Bilayer phantom fabrication and physical validation:} While the \gls{cad} model and numerical characterization of a bilayer phantom architecture have been completed, providing a theoretical framework and predicted system behavior, the physical fabrication and experimental validation of this design remain as future work. Fabricating the bilayer phantom with its external conductive shell and internal gelatine volume would enable direct experimental comparison with the numerical predictions, assessment of manufacturing tolerances and their impact on electrical behavior, and validation of the forward operator under realistic operating conditions.

\biblio % Needed for referencing to working when compiling individual subfiles - Do not remove
\end{document}
