% \subsection{Brain--Computer Interfaces}

The \gls{bci} Society adopted a working definition of a \gls{bci} as \emph{``a system that measures brain activity and converts it in (nearly) real-time into functionally useful outputs to replace, restore, enhance, supplement, and/or improve the natural outputs of the brain, thereby changing the ongoing interactions between the brain and its external or internal environments. It may additionally modify brain activity using targeted delivery of stimuli to create functionally useful inputs to the brain.''}~\cite{bci-soc}


In practical terms, a \gls{bci} provides a direct communication pathway between the brain and an external device, translating the user’s intentions---as reflected in their brain signals---into control commands without relying on normal neuromuscular pathways. Such systems can be used to replace or restore lost functions, for example enabling communication for individuals with severe motor impairments, or to enhance and supplement existing functions by allowing the brain to directly interact with external software or hardware~\cite{bci-soc}.

A typical \gls{bci} system operates as a processing pipeline composed of several stages. While implementation details vary across modalities and applications, these systems generally include signal acquisition, signal processing, command generation, and an application interface with feedback~\cite{wang-2025}. Together, these stages form a closed-loop system that enables the interpretation of neural activity and its translation into meaningful external actions.

Within this framework, the notion of a \gls{bci} paradigm plays a central role. A paradigm defines the mental task or stimulus structure through which user intent is encoded into measurable neural activity. As such, paradigm selection constitutes a fundamental design decision, as it directly influences the characteristics of the recorded signals, the processing strategies that can be applied, and the overall usability and performance of the system~\cite{wang-2025}.

\paragraph*{Signal Acquisition}
The signal acquisition stage involves capturing raw brain signals through a hardware--software interface. Brain activity can be recorded using non-invasive techniques (e.g., \gls{eeg}) or invasive approaches (e.g., electrocorticography), depending on application requirements and performance constraints. Among these, \gls{eeg} remains the most commonly used modality in \gls{bci} research due to its non-invasiveness and high temporal resolution. Regardless of the recording technique, the primary objective of this stage is to acquire neural data and stream it to subsequent processing steps~\cite{wang-2025}.

The choice of signal acquisition modality constrains the set of feasible \gls{bci} paradigms, as different techniques provide access to neural signals with varying spatial resolution, signal-to-noise ratio, and temporal characteristics. Consequently, signal acquisition and paradigm design cannot be treated as independent components, but must be considered jointly during system development~\cite{wang-2025}.

\paragraph*{Signal Processing}
Once acquired, brain signals are processed to extract information relevant to the user’s intention or cognitive state. This stage typically begins with preprocessing, in which raw recordings are cleaned to reduce noise and artifacts. Common operations include filtering to remove line noise or irrelevant frequency components, as well as attenuation of artifacts related to eye movements, muscle activity, or environmental interference. After preprocessing, the signal is assumed to provide a more reliable representation of the underlying neural activity.

Feature extraction is then performed on the preprocessed signals in order to identify signal characteristics that are informative for interpretation. At this level, signal processing strategies are commonly described in terms of the type of information they aim to recover. Passive processing approaches are primarily used for state monitoring and focus on neural patterns associated with involuntary or spontaneous states such as attention, mental workload, fatigue, or emotional state. These features are typically not associated with explicit user commands, but rather with the modulation of system behavior based on the user’s current state.

Active processing approaches, in contrast, aim to extract features that encode voluntary and intentional user actions. These features are used to generate explicit control commands and enable direct interaction with external devices. Depending on the paradigm and application, feature extraction may target self-generated neural activity or neural responses elicited by external stimuli. In this context, it is common to distinguish between endogenous and exogenous mechanisms. Endogenous mechanisms rely on voluntary, self-generated brain activity, such as motor imagery, where imagined movements induce modulations in sensorimotor rhythms through event-related desynchronization or synchronization in the mu and beta bands. Exogenous mechanisms, on the other hand, are stimulus-driven and exploit neural responses evoked by external inputs. For example, periodic visual stimulation can induce steady-state visually evoked potentials, characterized by oscillatory brain responses at the stimulation frequency, while infrequent or task-relevant stimuli can elicit event-related potentials such as the P300. In both cases, relevant features are extracted from the neural response in order to infer user intent~\cite{wang-2025}.

Once relevant features have been extracted, a classification step maps these features to discrete control states or decisions using statistical or machine learning methods. This classification process remains part of the signal processing stage and produces the interpreted output that is subsequently passed to the command generation and application interface. Hybrid approaches may combine multiple feature types or mechanisms, for example integrating state-related features with stimulus-driven responses, in order to improve robustness, increase the number of available control commands, or mitigate limitations of individual paradigms~\cite{wang-2025}.

Despite substantial advances in signal processing techniques, \gls{bci} performance remains constrained by factors such as inter-subject variability, training requirements, and the susceptibility of neural signals to noise and non-stationarities~\cite{wang-2025}.

\paragraph*{Command Generation}
Following feature extraction and classification, the command generation stage maps the recognized brain patterns to device-specific control signals. Depending on the application, this may involve selecting symbols, triggering discrete actions, or continuously controlling external devices such as cursors, robots, or assistive technologies~\cite{wang-2025}.

\paragraph*{Application and Feedback}
The final stage delivers the generated command to the external system and provides feedback to the user. Feedback may be visual, auditory, tactile, or multimodal, and plays a central role in supporting user learning and adaptation. Most \gls{bci} systems operate in a closed-loop configuration, in which feedback allows the user to adjust their mental strategy and contributes to improved system performance over time~\cite{wang-2025}.
