%-----------------------------------------------------------
% PDE
%-----------------------------------------------------------
We consider an EEG phantom composed of two contiguous regions—the inner gel volume and the 3D-printed head shell—together with the closed electrical circuit used for signal generation.

\subsubsection{Conductivity}
The phantom contains two conductive regions with distinct electrical properties: the saline–gelatin interior and the conductive PLA shell.


The solidified saline–gelatin mixture behaves as a linear, Ohmic conductor with
conductivity in the range $\sigma_{\text{gel}} \approx 0.3{-}0.4~\text{S/m}$~\cite{akor-2025}, comparable to
physiological saline and to values reported in electrophysiology phantom literature.

The outer shell is considered to be made of a commercially available conductive PLA filament~\cite{cpla}. The manufacturer's datasheet~\cite{cpla-datasheet} reports volume resistivities ($\rho$) ranging from $14.4~\Omega\!\cdot\!\mathrm{cm}$ to $33.6~\Omega\!\cdot\!\mathrm{cm}$ for printed test bars, with the exact value depending on both the printing temperature and the measurement orientation. For each tested temperature (210$^{\circ}$C and 230$^{\circ}$C), two resistivities are reported: one measured in the X–Y plane and one measured in the Z direction.

For the present work, the pair of values reported at $210^{\circ}\mathrm{C}$ is adopted to provide a consistent reference range: $19.2~\Omega\!\cdot\!\mathrm{cm}$ (X–Y direction) and
$33.6~\Omega\!\cdot\!\mathrm{cm}$ (Z direction). These values represent, respectively, the more conductive and the less conductive orientations of the printed material.

Converting resistivity $\rho$ to conductivity using $\sigma = 1/\rho$, and applying the unit conversion $1~\Omega\!\cdot\!\mathrm{cm} = 10^{-2}~\Omega\!\cdot\!\mathrm{m}$, yields conductivities in the approximate range
\[
\sigma_{\text{print}} \approx 3.0{-}5.2~\text{S/m}.
\]

Because these values reflect orthotropic measurements (planar vs.\ through-layer directions), the printed material is known to be electrically anisotropic: planar traces typically exhibit higher conductivity than the layer-normal direction. This behaviour is well documented in conductive-polymer additive manufacturing~\cite{akor-2025,tilve-martinez-2024,nowka-2024} and by the conductive PLA fabricant~\cite{cpla-datasheet}. Importantly, recent work shows that this anisotropy is not an intrinsic limitation; it can be significantly reduced through appropriate fabrication choices. For example, \cite{tilve-martinez-2024,tilve-martinez-2023} report that adjusting curing delays and resin temperature can diminish conductivity anisotropy by nearly two orders of magnitude, enabling the fabrication of electrically uniform 3D structures despite the layer-by-layer process. Comparable effects are observed in extrusion-based printing: \cite{paz-2020} shows that manufacturing parameters—such as layer thickness, extrusion width, screw speed, and extrusion temperature—strongly influence the electrical properties of the printed part. Likewise, \cite{nowka-2024} identifies path-planning variables, particularly infill pattern and infill angle, as key determinants of the resulting conductivity.


Collectively, these studies show that anisotropy in conductive polymers can be adjusted, sometimes dramatically, through processing, post-processing, curing strategies, and print-parameter selection. In practice, users fabricating the phantom may tune their printing conditions according to these guidelines to limit anisotropy as far as their equipment and workflow allow.

\subparagraph{Choice of $\sigma_{\text{shell}} = 4.1~\text{S/m}$.}
For the simulations, a concrete scalar value must be assigned to the shell conductivity. The datasheet values for printed test bars~\cite{cpla-datasheet} span approximately
$3.0$ to $5.2~\text{S/m}$, corresponding to the least and most conductive measurement directions. In this context, choosing the intermediate value
$\sigma_{\text{shell}} \approx 4.1~\text{S/m}$ serves as a balanced representative of a reasonably optimized print where the anistropy is already reduced, avoiding bias toward either the most conductive in–plane direction or the least conductive through–layer direction.

At the same time, the framework does not fix this value: $\sigma_{\text{shell}}$ is exposed as a user–defined parameter. Users who characterise their own printed material (or adopt specific print/curing strategies to further reduce anisotropy) can directly substitute their measured or preferred value, or perform parameter sweeps over the range $3{-}5.2~\text{S/m}$ to assess the sensitivity of their particular setup.

\subsubsection{Electrical insulation.} 
There are no prescribed current sources within the volume; all currents arise solely in response to the applied voltages. 
Any current injected by one internal electrode necessarily returns to the generator through another. 

Although the shell material is conductive, it is not connected to any external circuitry. 
The only interfaces with the outside are the EEG measurement electrodes placed on the shell surface, which --- as in any EEG system --- are assumed to have a very high input impedance. 
This makes the approximation of zero net current flow through them theoretically justified.

Consequently, the phantom can be modeled as an electrically insulated volume. 
This is expressed mathematically through homogeneous Neumann boundary conditions
\[
    \sigma\,\frac{\partial u}{\partial n} = 0,
\]
where $u$ is the electric potential (in volts), $\sigma$ is the electrical conductivity of the 
material at the boundary (in S/m), $n$ is the outward-pointing unit normal vector to the 
surface, and $\partial u / \partial n = \nabla u \cdot n$ denotes the normal derivative of 
the potential.

This condition simply states that no current flows out of the shell surface: the outward normal current density $J_n = \sigma\,(\partial u/\partial n)$ is zero at the exterior boundary~\cite{simscale-boundary-conditions}.

Physically, the phantom behaves as a closed volume conductor: currents injected inside must return inside, with no leakage into the air (which behaves as an excellent insulator at these field strengths).

External EEG electrodes used for recording do not inject current; they simply sample the surface potential. 
Real EEG amplifiers have input impedances on the order of $1$--$10~\text{M}\Omega$ or higher, so the current they draw is negligible~\cite{van-rijn-1990, jackson2014}

Thus, from the phantom’s perspective, a recording electrode is electrically passive: it does not clamp or perturb the surface potential. 
Accordingly, no Dirichlet or Neumann boundary condition is imposed at measurement locations; they are treated purely as observation points for $u$.

\subsubsection{Ohmic and Frequency Response Behavior.}

Over the frequency range of interest (DC to $\sim$100~Hz), the gel medium behaves as a linear, Ohmic conductor with negligible reactive (capacitive or inductive) effects. This is supported by experimental evidence from tissue-mimicking phantoms, which demonstrate frequency-independent conductivity across the EEG band~\cite{akor-2025}. For example, gelatin or saline phantoms typically exhibit less than 2\% variation in $\sigma$ from 0.1~Hz to 1~kHz, and negligible phase shift, confirming that conduction current dominates.~\cite{geddes-1967, Chandra2000}

% In physical terms, the displacement current density $\partial \mathbf{D}/\partial t$ remains much smaller than the conduction current $\mathbf{J}$ in this regime. This is formally justified by examining the ratio:

% \[
% \frac{|\partial \mathbf{D}/\partial t|}{|\mathbf{J}|} = \frac{\omega \varepsilon}{\sigma} \ll 1,
% \]

% as discussed in detail below. Consequently, dielectric storage and capacitive charging are negligible, and the medium can be considered purely resistive. This assumption is central to the quasi-static approximation, and is further justified in Section~\ref{subsection:maxwell} using Maxwell’s equations.

% \subsubsection{Summary of Assumptions}
% \nota{So, the assumptions made \textbf{up until now} are... and they are based in the system materials and previously explained bla bla bla
% Explain here why we do the "deprecitating of the displacement current" section later. or move it before and add it here... whats the best option? double check
% }

% \begin{itemize}
%     \item The phantom’s materials are linear, homogeneous conductors with
%     isotropic (effective) conductivity $\sigma(\mathbf{x})$ (piecewise constant: $\sigma_{\text{gel}}$ vs. $\sigma_{\text{shell}}$).
    
%     \item No internal current sources or sinks in the volume (all driving currents come from electrode boundary conditions).

%     \item No significant polarization or capacitive storage in the bulk (conductive current dominates over displacement current in the frequency range of interest).

%     \item Boundary conditions: Dirichlet ($u=V_i(t)$) on internal electrode surfaces; Neumann ($\sigma,\partial_n u=0$) on the external shell surface; no enforced condition for high-impedance measurement electrodes (they effectively float).

%     \item Interfaces between gel and shell are in perfect electrical contact (no contact impedance or gaps), so continuity conditions apply. \nota{this we didnt say before... do we keep it here? do i add a text saying those were the already said pnes and we introudce some new ones: etc etc }

% \end{itemize}


% With this system defined, we proceed to derive the governing partial differential equation (PDE) for the electric potential $u(\mathbf{x},t)$ in the domain $\Omega = \Omega_{\text{gel}} \cup \Omega_{\text{shell}}$.

\subsubsection{Summary of Assumptions}

To recap, the modelling choices made so far rely on a set of assumptions that were previously introduced and justified in the preceding subsections. For clarity, they are listed here in compact form:

\begin{itemize}
    \item The phantom materials are treated as linear, homogeneous conductors with isotropic \emph{effective} conductivity $\sigma(\mathbf{x})$, piecewise constant in each region ($\sigma_{\text{gel}}$ and $\sigma_{\text{shell}}$).

    \item No impressed current sources or sinks are present inside the volume: all currents originate from electrode boundary conditions.

    \item Displacement currents, capacitive storage, and polarization effects are negligible in the EEG frequency range, so conduction current dominates (quasi-static regime).

    \item Boundary conditions are defined as follows: Dirichlet ($u = V_i(t)$) on internal electrode surfaces, homogeneous Neumann ($\sigma\,\partial_n u = 0$) on the external shell surface,  
    and no enforced condition on high-impedance measurement electrodes (which electrically “float”).
\end{itemize}

In addition to these assumptions—which follow directly from material properties, fabrication details, and the quasi-static approximation—the following modelling simplifications are introduced for completeness:

\begin{itemize}
    \item \textbf{Interface continuity.}
    The gel and shell are assumed to be in perfect electrical contact (no gaps or interfacial
    impedance), so both the potential and the normal current density are continuous across
    their boundary. This reflects the physical construction—where the liquid gelatin–saline
    mixture is poured into the shell and solidifies against its inner surface—as well as the CAD
    procedure used to generate the simulation geometry, in which a ``boundary fill'' operation
    produces a watertight, conformal gel–shell interface.

    \item \textbf{Unified domain.}  
    The gel and shell are treated as parts of a single connected conductive domain $\Omega$, with only material parameters changing across regions. This allows the governing PDE to be written compactly over $\Omega = \Omega_{\text{gel}} \cup
    \Omega_{\text{shell}}$.
\end{itemize}

With these assumptions established, the derivation of the governing equation for the
electric potential $u(\mathbf{x},t)$ in the composite domain follows.


\subsubsection{From Maxwell’s Equations to governing PDE}
\label{subsection:maxwell}

We begin with Maxwell’s equations in differential form, appropriate for electromagnetic phenomena in the phantom. In particular, we use:

\paragraph*{Gauss’s law}
\[
\nabla\cdot \mathbf{D} = \rho_f
\]
where   
$\mathbf{D}$ is the electric displacement field (C/m$^{2}$) and 
$\rho_f$ is the free charge density (C/m$^{3}$).

There's no free charge in the conductive bulk (any charge separations are negligible in the voulme) therefore $\rho_f\approx 0 \Rightarrow \nabla\cdot \mathbf{D}\approx 0 $.

\paragraph*{Faraday’s law}
\[
\nabla\times \mathbf{E} = -\displaystyle\frac{\partial \mathbf{B}}{\partial t}
\]

where $\mathbf{E}$ is the electric field (V/m) and  $\mathbf{B}$ is the magnetic flux density (T).  


\paragraph*{Ampère’s circuital law}
\[
\nabla\times \mathbf{H} = \mathbf{J} + \displaystyle\frac{\partial \mathbf{D}}{\partial t}
\]
where $\mathbf{H}$ is the magnetic field intensity (A/m), $\mathbf{J}$ is the conduction current density (A/m$^{2}$) and $\partial \mathbf{D}/\partial t$ is the displacement current density (A/m$^{2}$).  

\paragraph*{Gauss’s law for magnetism}
\[
\nabla\cdot \mathbf{B} = 0
\]
where $\mathbf{B}$ is the magnetic flux density (T).  

We now invoke the quasi-static approximation appropriate for bioelectric systems like EEG~\cite{troparevsky-2010, nunez-2025}. This approximation is justified when both temporal and spatial variations of the fields are sufficiently slow, so that wave propagation effects can be neglected. In this case, the highest relevant frequency (100 Hz) corresponds to a wavelength larger than 300\space km for both materials (as shown in Appendix~\ref{appendix:wavelength}). The effective wavelength remains many orders of magnitude larger than the phantom’s size (around 0.3~m). 
% maybe we leave this commented, but this is the explanation for lambda ...
% The wavelength $\lambda$ computed in Appendix~A quantifies the distance over which an electromagnetic wave completes one full oscillation at the highest frequency of interest (here, 100~Hz). In wave–propagating regimes, field quantities can vary significantly over distances comparable to $\lambda$. Conversely, when $\lambda$ is much larger than the physical dimensions of the system, spatial variations become negligible and the fields behave in an effectively instantaneous, diffusion–like manner rather than as travelling waves. Appendix~A shows that, even under conservative assumptions for the materials’ permittivity, the resulting wavelengths (tens to hundreds of kilometres) exceed the phantom's characteristic size ($\sim 0.3$~m) by more than five orders of magnitude. This disparity confirms that wave propagation effects cannot develop within the phantom, thereby validating the electroquasistatic treatment adopted in this section.
This places the system deep within the electroquasistatic regime, where the electromagnetic fields adjust effectively instantaneously across the volume.

Consequently, the spatial phase variation of the electric field is negligible, and potential changes propagate uniformly. Empirical EEG observations support this: “potentials show no measurable time delay between physically separated regions” \cite{nunez-2025}. This allows us to neglect the wave nature of the field and adopt a quasi-static treatment in which the electric field is determined solely by local sources (none in this case) and boundary conditions.

In Ampère’s law, the total current includes both the conduction current density $\mathbf{J}$ and the displacement current density $\partial \mathbf{D}/\partial t$.  At low frequencies in conductive media, the displacement current is negligible compared to the conduction current. The criterion for this is:

\[
\frac{|\partial \mathbf{D}/\partial t|}{|\mathbf{J}|} = \frac{\omega \varepsilon}{\sigma} \ll 1
\]

where $\omega = 2\pi f$ is the angular frequency, $\varepsilon$ is the absolute permittivity of the medium, and $\sigma$ its conductivity.

For biological-like media such as a gel phantom made from solidified gelatin with salt in water, this condition holds robustly. Even a small amount of salt raises conductivity to $\sigma \sim 0.3$ S/m, while water-based media at 100 Hz can have effective permittivities on the order of $10^6 \varepsilon_0$~\cite{abraham-1996,plonsey-1967}. This yields:

\[
\omega\varepsilon \approx 2\pi \cdot 100 \cdot 10^6 \cdot \varepsilon_0 \approx 0.0056\ \text{S/m} 
\]

Since $\sigma \gg \omega \varepsilon$, the displacement current can be ignored. The resulting approximation is:

\[
\nabla \times \mathbf{H} \approx \mathbf{J}
\]

This quasi-static form of Ampère’s law is standard in low-frequency biophysics and electrophysiology~\cite{mognaschi-2016}, and reflects that all relevant current arises from conduction. In this regime, capacitive effects of the material are negligible: its electrical response is effectively resistive, and any residual capacitance is too small to produce any appreciable effect on the system~\cite{phillips-2007}.

Moreover, the general form of the low-frequency approximation is:

\[
\nabla \times \mathbf{H} = \mathbf{J}_0 + \sigma \mathbf{E}
\]

where $\mathbf{J}_0$ is any impressed (source) current and $\sigma \mathbf{E}$ is the conduction current density~\cite{mognaschi-2016}. In our case, $\mathbf{J}_0 = 0$ in passive regions, so the equation simplifies to:

\[
\nabla \times \mathbf{H} = \sigma \mathbf{E}
\]


We also assume the electromagnetic induction term in Faraday’s law is negligible. That is, $\nabla\times \mathbf{E} \approx -\partial_t \mathbf{B} \approx 0$. Physically, the currents in our phantom (and in the head) are so slowly varying that they do not produce significant time-varying magnetic flux; any induced electric field from changing $\textbf{B}$ is extremely small compared to the electrostatic field. Under this assumption:
\[
\nabla\times \mathbf{E} \;\approx\; \mathbf{0} \label{faraday-qs}
\]
Therefore, we can define $u(\mathbf{x},t)$ such that
\[
E= ~- \nabla u(\mathbf{x},t).
\]


Iin EEG contexts, the zero-curl condition holds to very high accuracy, enabling the use of an electrostatic potential~\cite{nunez-2025,troparevsky-2010}

At this point, we have reduced Maxwell’s laws to a simplified electroquasistatic form applicable to the phantom:
\begin{itemize}
    \item $\nabla\cdot \mathbf{D} \approx 0$ 
    \item $\nabla\times \mathbf{E} \approx 0 \Rightarrow \mathbf{E}=-\nabla u$.
    \item $\nabla\times \mathbf{H} = \mathbf{J}$ 
    \item  $\nabla\cdot \mathbf{B}=0$ 
\end{itemize}

In conductive media, the current density $\mathbf{J}$ is related to the electric field by Ohm’s law:
\[
\textbf{J}(\textbf{x},t) = \sigma(\textbf{x})\, \textbf{E}(\textbf{x},t)
\]

Combining Ohm’s law with $\mathbf{E}=-\nabla u$, we get the current density in terms of the potential:

\[
\textbf{J}(\textbf{x},t) = -\,\sigma(\textbf{x})\,\nabla u(\textbf{x},t) \label{eq:JgradU}
\]

% We now enforce charge conservation in differential form. Maxwell’s equations include the continuity equation $\nabla\cdot \mathbf{J} + \partial \rho_f/\partial t = 0$. In steady or slowly varying conduction, no net charge builds up in any region (any small charge separations that do occur serve only to maintain the electric field in steady state, but do not accumulate over time). Thus $\partial_t \rho_f \approx 0$. Consequently:

% \[
% \nabla \cdot \textbf{J}(\textbf{x},t) = 0, \qquad\text{for all } \mathbf{x}\in \Omega_{\text{gel}}\cup\Omega_{\text{shell}}\label{eq:continuity}
% \]

% This condition simply states that electric current does not accumulate within the volume: whatever current enters a small region must also leave it. 

% Finally, substituting the expression for the current density from
% Eq.~\eqref{eq:JgradU} into the continuity relation in
% Eq.~\eqref{eq:continuity} leads to the governing equation used in the
% simulations:
% \[
% -\nabla \cdot \big(\sigma(\mathbf{x})\, \nabla u(\mathbf{x},t)\big) = 0,
% \qquad \text{for all } \mathbf{x}\in \Omega_{\text{gel}}\cup\Omega_{\text{shell}}.
% \tag{PDE}
% \]

We now enforce charge conservation in differential form. Maxwell’s equations 
include the continuity equation $\nabla\cdot \mathbf{J} + \partial \rho_f/\partial t = 0$. 
In steady or slowly varying conduction, no net charge builds up in any region 
(any small charge separations that do occur serve only to maintain the electric 
field, but do not accumulate over time). Thus $\partial_t \rho_f \approx 0$, and

\[
\nabla \cdot \mathbf{J}(\mathbf{x},t) = 0,
\qquad\text{for all } \mathbf{x}\in \Omega_{\text{gel}}\cup\Omega_{\text{shell}}.
\tag{5.3.5}\label{eq:continuity}
\]

This condition simply states that electric current does not accumulate in the 
volume: whatever current enters a small region must also leave it.

Finally, substituting the expression for the current density from 
Eq.~\eqref{eq:JgradU} into the continuity relation in 
Eq.~\eqref{eq:continuity} leads to the governing equation used in the simulations:
\[
-\nabla \cdot \big(\sigma(\mathbf{x})\, \nabla u(\mathbf{x},t)\big) = 0,
\qquad \text{for all } \mathbf{x}\in 
\Omega_{\text{gel}}\cup\Omega_{\text{shell}}.
\tag{PDE}
\]


\nota {1. mencionar que esto es coherente con otrs trabajos similares en la literattura como cancelli (10.1088/1741-2560/13/3/036022)}