%-----------------------------------------------------------
% Phantom-Head Transfer Model
%-----------------------------------------------------------

Having established the physical model of the phantom and the quasi-static PDE
governing its behaviour, the next step is to construct a purely numerical
representation of the system. In this section we no longer work with Maxwell’s
equations or the FEM solver directly; instead, we treat the simulated results as
the “ground-truth’’ behaviour of the phantom and build a linear model that maps
voltages applied to the \emph{internal electrodes} to the potentials measured at
the 21 \emph{scalp probes}.

Our objective is to express this relationship in the compact form
\begin{equation}\label{eq:forward-operator}
V_{\text{scalp}} = A\,V_{\text{electrode}},
\end{equation}
where \(V_{\text{electrode}}\) contains the voltages that can be actively imposed on the
nine internal electrodes, and \(A\) is an effective forward operator derived from
the FEM simulations. This linear model allows us to predict scalp potentials
resulting from arbitrary internal stimulation patterns.

In practice, however, the intended use of the system is the inverse one: the
user specifies a desired potential pattern on the scalp probes, and we seek the
internal electrode voltages that best reproduce it. Because nine controllable
electrodes must reproduce twenty-one probe measurements, the inverse problem is
inherently underdetermined and the matrix \(A\) is not invertible. For this
reason, the solution is obtained through a conditioned pseudoinverse of \(A\),
which yields the internal voltages that minimise the reconstruction error at the
scalp while maintaining numerical stability.

\subsubsection{Rationale for using dipoles instead of single-electrode stimulation}

Before constructing the numerical model, we evaluated a ``monopolar''
stimulation protocol in which a single internal electrode was set to
\(+1~\mathrm{V}\) while the remaining eight were held at \(0~\mathrm{V}\),
following the procedure described in \cite{CITE-LATER cuando me encuentre en donde anote la fuente}. For each of the nine
electrodes, the resulting potentials at the 21 scalp probes were obtained from
the FEM simulations.

A consistent and problematic phenomenon appeared: although the absolute voltage
levels differed across probes, the \emph{pattern} of probe responses was almost
independent of which electrode was activated. In practical terms, every
monopolar excitation produced nearly the same 21-dimensional output vector. This
renders the forward operator associated with monopolar stimulation extremely
poorly conditioned, since its nine columns are nearly collinear. Such a system
cannot support meaningful inversion or reconstruction.

This behaviour is consistent with the geometry and scale of the phantom: at the
distance of the scalp probes, the spatial electric field patterns produced by
individual electrodes become very similar, making it difficult for a probe to
distinguish which electrode was responsible for the excitation. For the purposes
of inversion, the monopolar protocol therefore provides insufficient independent
information.

To address this limitation, we instead use \emph{dipolar} stimulation. A dipole
creates a stronger spatial gradient in the electric field due to the opposing
polarities of its two electrodes. This gradient enhances the sensitivity of scalp
measurements to the specific location and orientation of the dipole source.
Consequently, different dipole configurations produce probe patterns that are
more distinguishable from one another. This controllable dependence on the
stimulation source improves the conditioning of the forward operator \(A\),
enabling more robust inverse reconstruction.

A dipole is defined by selecting a pair of distinct
electrodes \((e_i,e_j)\), and, for definiteness, we always label them so that
\(i<j\). Under a fixed polarity convention, electrode \(e_i\) is set to
\(+1~\mathrm{V}\), electrode \(e_j\) to \(-1~\mathrm{V}\), and all remaining
electrodes are held at \(0~\mathrm{V}\):
\[
u_{e_i} = +1~\mathrm{V},\qquad 
u_{e_j} = -1~\mathrm{V},\qquad 
u_{e_k}=0~\mathrm{V}\ \text{for } k\neq i,j.
\]
% The ``ordered'' condition \(i<j\) is used solely to avoid duplicates; mathematically,
% the physical dipole is defined by this exact polarity convention.

With nine electrodes, every unordered pair of distinct electrodes generates one
dipole. The number of such pairs is
\[
\binom{9}{2} = \frac{9\cdot 8}{2} = 36.
\]
Each of these 36 dipoles produces a spatially distinct electric field pattern,
leading to substantially different scalp voltage distributions. The resulting
probe responses are far more dipole-dependent than those obtained from monopolar
stimulation: each dipole generates a characteristic signature at the scalp that
can be more easily distinguished from the others. Although the 36 dipole
orientations span only a three-dimensional physical space and therefore contain
some degree of redundancy, they yield a forward operator \(A\) with significantly
improved conditioning, making the system amenable to inversion.

\subsubsection{Forbidden triads: definition, interpretation, and general form}

Dipoles encode strict pairwise voltage differences: a dipole \((e_i,e_j)\)
imposes \(u_{e_i} > u_{e_j}\) under our fixed \(+1/-1\) convention. When several
dipoles are selected simultaneously, the electrode voltages must satisfy all
their pairwise inequalities at once.

A \emph{forbidden triad} (FT) is a set of three dipoles involving the same
triplet of electrodes, whose required pairwise inequalities cannot all be
satisfied by any assignment of scalar voltages to the electrodes.

Formally, for three distinct electrodes \(e_i,e_j,e_k\), the dipoles
\[
(e_i,e_j),\qquad (e_i,e_k),\qquad (e_j,e_k)
\]
constitute a forbidden triad. Under our sign convention, they impose:
\[
u_{e_i} > u_{e_j}, \qquad
u_{e_i} > u_{e_k}, \qquad
u_{e_j} > u_{e_k}.
\]
Taken individually, each inequality is valid; however, together they imply two
requirements that cannot be simultaneously satisfied with the fixed voltage
offsets forced by dipoles. In other words, no choice of electrode voltages
\(\{u_{e_i}\}\) can generate these three dipoles at once.

More generally, for any distinct \(i<j<k\), the triad
\[
\{(e_i,e_j),\ (e_i,e_k),\ (e_j,e_k)\}
\]
is forbidden. Any dipole-selection algorithm must therefore avoid selecting all
three dipoles from such a triplet.

We will refer to these structures as \emph{forbidden triads} throughout the
remainder of this work. Enforcing their exclusion ensures that the selected
dipoles always correspond to a physically realisable set of electrode voltages.

\subsubsection*{Transition to the algebraic model}

\nota{Lo que sigue es un \textit{fancy} borrador de la idea, falta explicar más y ajustar cosas.}
\nota{Básicamente, la matriz A que definimos antes, deja de ser "lo que sea que sea A" y le damos dimensiones, valores e interpretación física de que representa, cómo se obtiene y planea optimizar}

We will use \textbf{one} equation for \textbf{all} cases:

\[
\boxed{
V_{\text{scalp}}^{(w)} \;=\; W \, F \, S \, B \, V_{\text{antena}}
}
\]

where:

\begin{itemize}
  \item $V_{\text{antena}} \in \mathbb{R}^{9\times 1}$:  
  antenna voltage vector; values that can be set on the 9 internal electrodes. Units: V 
  
  \item $B \in \mathbb{R}^{36\times 9}$:  
  \textbf{antenna $\to$ dipole} difference matrix.  
  Each \textbf{row} corresponds to one dipole $(e_x, e_y)$: it has $+1$ in column $x$, $-1$ in column $y$, and $0$ elsewhere.

  \item $S \in \mathbb{R}^{36\times 36}$:  
  \textbf{selection / mask matrix} (diagonal).
  \begin{itemize}
    \item $S_{jj} = 1$: dipole $j$ is \textbf{enabled}.
    \item $S_{jj} = 0$: dipole $j$ is \textbf{disabled}.
  \end{itemize}
  Each selection algorithm returns such an \texttt{S}.

  \item $F \in \mathbb{R}^{21\times 36}$:  
  \textbf{dipole $\to$ scalp} transfer matrix (this is the one already computed from the 36 unit-dipole simulations).  
  Column $j$ of $F$ is the 21-probe response to dipole $j$ excited with $\pm 1$ V.

  \item $W \in \mathbb{R}^{21\times 21}$:  
  \textbf{probe-weighting} matrix (diagonal).
  \begin{itemize}
    \item $W = I_{21}$ $\to$ unweighted model
    \item $W \neq I_{21}$ $\to$ emphasize/de-emphasize regions (frontal, occipital, etc.)
  \end{itemize}

  \item $V_{\text{scalp}}^{(w)} \in \mathbb{R}^{21\times 1}$:  
  weighted scalp voltages predicted by the model.
\end{itemize}

So, the data flow is:

\begin{enumerate}
  \item \textbf{antennas} $\to$ $B V_{\text{antena}}$ $\to$ \textbf{dipole amplitudes}
  \item dipoles $\to$ $S (B V_{\text{antena}})$ $\to$ \textbf{only allowed/selected dipoles}
  \item selected dipoles $\to$ $F S B V_{\text{antena}}$ $\to$ \textbf{scalp voltages}
  \item scalp voltages $\to$ $W F S B V_{\text{antena}}$ $\to$ \textbf{weighted scalp voltages}
\end{enumerate}

\nota{Sobre W: opcional, quizás luego solo usamos W=I21 en el desarrollo del proyecto}.


\subsubsection*{Why masking \textbf{B} and not \textbf{F}?}

\begin{itemize}
  \item masking \textbf{B} via $S B$ keeps the original \textbf{F} intact — no duplications;
  \item mathematically:
  \[
  F \, S \, B = F \, (S B)
  \]
  because matrix multiplication is associative;
  \item disabling a dipole means: ``this dipole will \textbf{never} be produced from any antenna voltage'' $\to$ that is naturally a constraint on the \textbf{dipole-generation} side (\texttt{B}), not on the measurement side (\texttt{F});
  \item selection algorithms can therefore \textbf{always} return $S_{alg}$.
\end{itemize}

\bigskip

\subsubsection{Selection algorithms}

All algorithms described below operate on the same base matrices defined previously:
the dipole $\rightarrow$ scalp matrix $F$, the antenna $\rightarrow$ dipole matrix $B$,
and the optional probe weighting matrix $W$.

Each algorithm builds a list of selected dipoles
\(\text{selected} = \{(i,j), (k,l), \dots\}\)
subject to the physical constraint that no forbidden triad
\(\{(i,j), (i,k), (j,k)\}\)
is ever formed.  
The output of each algorithm is a diagonal selection (mask) matrix \(S \in \mathbb{R}^{36\times36}\)
whose diagonal entries are one for selected dipoles and zero otherwise.
The mask \(S\) is applied on the dipole–generation side of the system,
yielding $M = W \cdot F \cdot S \cdot B$ as the effective forward model.

\nota{
Para cada algoritmo de selección hay que explicar mínimamente:
\begin{itemize}
  \item \textbf{Objetivo:} qué busca optimizar el algoritmo (ej: minimizar $\kappa$, maximizar cobertura espacial, etc.)
  \item \textbf{Justificación:} por qué ese criterio mejora el sistema (ej: reducir $\kappa$ mejora la estabilidad numérica del pseudoinverso)
  \item \textbf{Procedimiento:} pasos del algoritmo (1. inicializar con..., 2. en cada iteración..., 3. criterio de parada...)
  \item \textbf{Parámetros:} qué inputs recibe el algoritmo (ej: número máximo de dipolos, umbral de tolerancia, etc.)
  \item \textbf{Output:} la matriz diagonal $S$ con los dipolos seleccionados
\end{itemize}
}


\nota{
Luego iría la sección con la definición de pseudoinversa (anotada en apuntes) y en resultados se mostrarían 
los resultados de cada algoritmo/los mejores algoritmos y sus comparaciones: dipolos seleccionados, error al reconstruir el sistema, 
número de condición, rango, etc.

\textbf{Comparaciones/validaciones a realizar:}
\begin{enumerate}
  \item \textbf{Validación del modelo directo (forward):} 
  \[
  \|V_{\text{out}}^{\text{solver}} - V_{\text{out}}^{\text{matriz}}\| = \|V_{\text{out}}^{\text{solver}}(V_{\text{in}}) - (A \cdot V_{\text{in}})\| \approx 0
  \]
  Comparar la respuesta del solver FEM vs. la del sistema matricial $A = WFSB$ ante la misma entrada $V_{\text{in}}$, 
  para varios casos de voltajes de entrada.
  
  \item \textbf{Validación del modelo inverso (reconstruction):} 
  \[
  \|V_{\text{in}}^{\text{solver}} - A^{\dagger} \cdot V_{\text{out}}^{\text{solver}}\| \approx 0
  \]
  Meter un $V_{\text{in}}$ conocido al solver, obtener $V_{\text{out}}^{\text{solver}}$, y verificar que 
  al aplicar la pseudoinversa $A^{\dagger}$ al output del solver, se recupera el $V_{\text{in}}$ original.
  
  \item \textbf{Métricas de condicionamiento:} Número de condición $\kappa(M)$, rango efectivo, valores singulares.
  
  \item \textbf{Otras métricas potencialmente relevantes:} Error RMS entre patrones de voltaje, cobertura espacial 
  de los dipolos seleccionados, sensibilidad a ruido en las mediciones, robustez ante variaciones de conductividad, etc.
\end{enumerate}
}